Timing and Positioning: Insights from Steak-Related Product Pricing at Walmart and Loblaws

### 2024-12-04 paper/paper.qmd
Update paper.qmd

```{r}
#| label: fig-bll1
#| fig-cap: Current prices of steak-related products by vendor and month, showing Walmart's consistent lower pricing and Loblaws' broader range with seasonal price fluctuations.
#| echo: false
#### Read data ####
analysis_data <- read_parquet("/Users/lucky/Desktop/Explore-steak-related-products/data/02-analysis_data/analysis_data.parquet")

@@

analysis_data <- read_parquet("/Users/lucky/Desktop/Explore-steak-related-products/data/02-analysis_data/analysis_data.parquet")

>>>>

```{r}
#| label: fig-bll1
#| fig-cap: Current prices of steak-related products by vendor and month, showing Walmart's consistent lower pricing and Loblaws' broader range with seasonal price fluctuations.
#| echo: false
#### Read data ####
analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")

@@

analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
